R for Clinical Study Reports and Submission

### 2021-09-16 index.Rmd
General updates to improve flow and fixed typos.

Welcome to R for clinical study reports and submission. 
Clinical study reports (CSR) are essential parts of clinical trials development. 
a CSR is an "integrated" full scientific report of an individual clinical trial.

The [ICH E3: structure and content of clinical study reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf) 
provide guidance to assist sponsors in the development of a CSR. 
In this book, you will learn how to use R to prepare CSR and submit to regulatory agencies.

@@

```{r, echo = FALSE}
contributors <- c(person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"), 
                  person("Nan", "Xiao", role = "aut"), 
                  person("Keaven", "Anderson", role = "aut"),
                  person("Yujie", "Zhao", role = "ctr"), 
                  person("Aiming", "Yang", role = "ctr"))
```

>>>>

Welcome to R for clinical study reports and submission. 
Clinical study reports (CSR) are essential parts of clinical trial development. 
A CSR is an "integrated" full scientific report of an individual clinical trial.

The [ICH E3: structure and content of clinical study reports](https://database.ich.org/sites/default/files/E3_Guideline.pdf) 
provides guidance to assist sponsors in the development of a CSR. 
In this book, you will learn how to use R to prepare a CSR and how to submit it to regulatory agencies.

@@

```{r, echo = FALSE}
contributors <- c(person("Yilong", "Zhang", email = "yilong.zhang@merck.com", role = "aut"), 
                  person("Nan", "Xiao", role = "aut"), 
                  person("Keaven", "Anderson", role = "aut"),
                  person("Yujie", "Zhao", role = "ctr"), 
                  person("Aiming", "Yang", role = "ctr",
                  person("Steven", "Haesendonckx", role = "ctr")))
```

### 2021-09-16 intro.Rmd
address Aiming's comments
General updates to improve flow and fixed typos.

In clinical trial development, developers need to organize source code to deliver 
Study Data Tabulation Model (SDTM) or Analysis Dataset Model (ADaM) datasets 
and tables, listings, and figures (TLFs).
For example, a Phase 3 clinical trial typically requires hundreds of TLFs. 
A consistent and well-defined folder structure is crucial 
to managing a clinical trial analysis and reporting (A&R) project.

We recommend using R package folder structure to organize all the A&R related 
source code and documentation for a clinical trial A&R project. 
By using the R package folder structure, 
you can follow the convention to organize your code as other contributors on CRAN.
This consistent approach simplifies the communication for all developers 
within and across organizations.

@@

In addition, R package folder structure is also recommended 
to develop Shiny app as discussed 
in [Chapter 20 of Master Shiny](https://mastering-shiny.org/scaling-packaging.html) book 
and [Engineering Production-Grade Shiny Apps](https://engineering-shiny.org/golem.html) book.

@@

- Part 1, "Delivering TLFs in CSR" provides general information with examples 
to create tables, listings, and figures. 
In this part, we assume readers are individual contributors to a clinical project
with some experience in R programming. 
We expect readers are familiar with data manipulation in R. 
Some good reference includes [Hands-On Programming with R](https://rstudio-education.github.io/hopr/),
[R for Data Science](https://r4ds.had.co.nz/) and 
[Data Manipulation with R](https://www.amazon.com/Data-Manipulation-R-Use/dp/0387747303).

@@

- Part 3, "eCTD Submission package"
provides general information in preparing 
submission package related to clinical study report (CSR) in 
electronic Common Technical Document (eCTD). 
In this part, we assume a reader is a project lead of a clinical project 
with experience in R package development as well.

>>>>

In clinical trial development, source code needs to be developed and maintained to generate and deliver 
Study Data Tabulation Model (SDTM), Analysis Dataset Model (ADaM) datasets and tables, listings, and figures (TLFs).
A typical example is a Phase 3 clinical trial where hundreds of TLFs are required for submission. 
Considering the amount of programs required for such an effort, a consistent and well-defined folder structure is crucial in managing a clinical trial analysis and reporting (A&R) project.

During the course of this book we will provide a recommended folder structure that is aligned with CRAN submissions of R packages.

@@

In addition, R package folder structure is also recommended 
to develop Shiny apps as discussed 
in [Chapter 20 of Master Shiny](https://mastering-shiny.org/scaling-packaging.html) book 
and [Engineering Production-Grade Shiny Apps](https://engineering-shiny.org/golem.html) book.

@@

- Part 1, "Delivering TLFs in CSR" provides general information with examples 
to create tables, listings, and figures. 
In this part, we assume readers are individual contributors to a clinical project
with some experience in R programming. 
We expect readers are familiar with data manipulation in R. 
Some good references include [Hands-On Programming with R](https://rstudio-education.github.io/hopr/),
[R for Data Science](https://r4ds.had.co.nz/) and 
[Data Manipulation with R](https://www.amazon.com/Data-Manipulation-R-Use/dp/0387747303).

@@

- Part 3, "eCTD Submission package"
provides general information in preparing 
submission package related to clinical study report (CSR) in 
electronic Common Technical Document (eCTD). 
In this part, we assume a reader is a project lead of a clinical project 
with experience in R package development and submission.
